Joint photometric modeling for improved measurements in imaging surveys.

### 2014-11-13 documents/paper/ms_v0.0.tex
doc update

\begin{itemize}
\item Mixture of Gaussians where each datum's observational uncertainty is accounted for.
\item cite bovy and applicable works.
\item regularization to avoid singularities
\end{itemize}

\subsection{Posterior estimation}

>>>>

Our goal is to construct a model of the joint distribution of the space of
possible photometric measurements.  The key idea is that once we have learned
what the underlying distribution can be, we can utilize this knowledge as a
prior distribution over what the set of \emph{true} observations should be for
a given object.  That is, for each datum we want to construct the posterior
for the true photometric quantities -

\noindent where $\datum$ is the observed vector of photometric measurements, 
$\truedatum$ is the set of values we would have observed in the absense of
noise, and $\datumcov$ is the covariance for the observation which is
constructed from our (e.g, the survey's) noise estimates.  The distribution 
$p(\truedatum)$ is the prior distribution we wish to learn, and the likelihood
$p(\datum | \truedatum)$ is assumed to be Gaussian.  Since we are learning the
prior distribution from a set of many observations, this is refered to as a
multilevel or hierarchical model.

The art in building a hierachical model is deciding the structure of the
distributions involved -- how distributions are parameterized, what is held
fixed or considered know, and what the relationships are between the various
distributions.  We believe the distribution of $p(\truedatum)$ can be quite 
complex, and it is not obvious what the right description of the distribution
might be.  For these reasons, we choose to use Extreme Deconvolution
